The importance of measurement uncertainty in ecological management

### 2017-12-14 manuscripts/manuscript.Rmd
refs

In the case of no uncertainty, the optimal harvest strategy is to reduce the population to the size at which it obtains the maximum growth rate, known as Biomass at Maximum Sustainable Yield, $B_{MSY}$ (this is adjusted slightly in the case of economic discounting of future profits, but is otherwise quite general, see @ClarkTextbook). For the Graham-Schaefer model (and many others), this is achieved at $B_{MSY} = K/2$, with a corresponding annual harvest of $H_{MSY} = r K / 4$.

@@

The resulting solutions only deepened the paradox, rather than recovering a more cautious policy in response to the uncertainty, @Clark1987 finds policies that are often *less* cautious:

@@

Numerically, each of these functions are defined over a discrete set of possible states, observations, and actions, and can thus be represented as a collection of matrices or tensors.  As in the case of MDP [@Marescot2013], the POMDP problem can be solved by existing and well-studied algorithms. While not unknown to the conservation literature [@Williams2009], algorithms for POMDP have historically scaled quite poorly, and their application has been restricted to contexts with only a handful of possible states and actions [e.g. @Chades2008; @Chades2011; @Fackler2014; @Fackler2014b].  POMDP algorithms remain a very active area in artificial intellegence, and by adapting recent algorithmic developments [@Kurniawati2008] from that field we are able to find solutions for the considerably more complex problems such as the case of fisheries managment, which requires on the order of 100 states and actions to provide sufficient numerical resolution. Readers interested in the technical details of these algorithms should consult the extensive literature in in POMDP methods. For those interested in exploring or applying these methods, we have developed a preliminary R package, @sarsop, which can be used to replicate any of the results presented here and explore other variations.

>>>>

In the case of no uncertainty, the optimal harvest strategy is to reduce the population to the size at which it obtains the maximum growth rate, known as Biomass at Maximum Sustainable Yield, $B_{MSY}$ (this is adjusted slightly in the case of economic discounting of future profits, but is otherwise quite general, see @Clark1990). For the Graham-Schaefer model (and many others), this is achieved at $B_{MSY} = K/2$, with a corresponding annual harvest of $H_{MSY} = r K / 4$.

@@

The resulting solutions only deepened the paradox, rather than recovering a more cautious policy in response to the uncertainty, @Clark1986 finds policies that are often *less* cautious:

@@

Numerically, each of these functions are defined over a discrete set of possible states, observations, and actions, and can thus be represented as a collection of matrices or tensors.  As in the case of MDP [@Marescot2013], the POMDP problem can be solved by existing and well-studied algorithms. While not unknown to the conservation literature [@Williams2011], algorithms for POMDP have historically scaled quite poorly, and their application has been restricted to contexts with only a handful of possible states and actions [e.g. @Chades2008; @Chades2011; @Fackler2014; @Fackler2014b].  POMDP algorithms remain a very active area in artificial intellegence, and by adapting recent algorithmic developments [@Kurniawati2008] from that field we are able to find solutions for the considerably more complex problems such as the case of fisheries managment, which requires on the order of 100 states and actions to provide sufficient numerical resolution. Readers interested in the technical details of these algorithms should consult the extensive literature in in POMDP methods. For those interested in exploring or applying these methods, we have developed a preliminary R package, @sarsop-pkg, which can be used to replicate any of the results presented here and explore other variations.
